Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-06-10 cordillera-cycle.tex
Update discussion subsection titles.
Introduce 6-km resolution in text.

PISM is a~shallow model, which implies that the balance of stresses is
approximated based on their predominant components.
The Shallow Shelf Approximation (SSA) is used as a ``sliding law'' for the
Shallow Ice Approximation (SIA) \citep{bueler-brown-2009,winkelmann-etal-2011}.
SIA and SSA velocities are computed by finite difference methods on a~10\,km
resolution horizontal grid of 300 by 150 points (the modelling domain). Ice
softness depends on temperature and water content through an enthalpy
formulation \citep{aschwanden-blatter-2009,aschwanden-etal-2012}. Enthalpy is
computed in three dimensions in up to 51 layers within the
ice, and temperature is additionally computed in 31 layers in bedrock to
a~depth of 3\,km. Surface air temperature from the atmospheric forcing
provides the upper boundary condition to the ice enthalpy model, and
a~geothermal heat flux of 70\,\unit{mW\,m^{-2}} provides the lower boundary
condition to the bedrock thermal model. Although this uniform value does not
account for the high spatial geothermal variability in the region, it is on
average representative of available heat flow measurements
\citep{artemieva-mooney-2001,blackwell-richards-2004}.

@@

@@

\subsection{Timing of the glacial maxima}

@@

\subsection{Glaciated areas through the last glacial cycle}

@@

\subsection{History of the last deglaciation}

>>>>

PISM is a~shallow model, which implies that the balance of stresses is
approximated based on their predominant components.
The Shallow Shelf Approximation (SSA) is used as a ``sliding law'' for the
Shallow Ice Approximation (SIA) \citep{bueler-brown-2009,winkelmann-etal-2011}.
Ice softness depends on temperature and water content through an enthalpy
formulation \citep{aschwanden-blatter-2009,aschwanden-etal-2012}. Surface air
temperature from the atmospheric forcing provides the upper boundary condition
to the ice enthalpy model. Temperature is computed subglacially to a~depth of
3\,km, where it is conditioned by a~geothermal heat flux of
70\,\unit{mW\,m^{-2}}. Although this uniform value does not
account for the high spatial geothermal variability in the region, it is on
average representative of available heat flow measurements
\citep{artemieva-mooney-2001,blackwell-richards-2004}.

@@

For all records, we firstly run a low-resolution simulation, using
a~10\,\unit{km}, 300 by 150~points horizontal grid for SSA and SIA velocities,
up to 51~enthalpy layers in the ice, and 31~temperature layers in the bedrock.
For the GRIP and EPICA records, we then run a second simulation using a higher
horizontal resolution of 6\,\unit{km}, up to 101~ice layers, and 61~bedrock
layers.

@@

\subsection{Timing of the glaciation peaks}

@@

\subsection{Spatial imprint of ice cover}

@@

\subsection{Deglaciation history}
